A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-15 src/paper.tex
iTV Environment section

- set-top box

- Service discovery

- context synchronization

- presence detector

>>>>

The iTV environment consists of an iTV terminal, which can be an set-top box or some iTV terminal with some sort of communication technology e.g., WiFi or Bluetooth. This environment has some services to facilitate the communication with second screen devices. The first one is the Presence Detector Service (PDS), which is in charge of discovering nearby second screen devices. The PDS is connected with another service known as Profile Handler Service (PHS), which aims to perform profile management at each moment when new second screen devices are found in the iTV environment.
